Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{EIP-150 revision (\YellowPaperVersionNumber{})}}

### 2017-10-02 Paper.tex
Deleting extra }

%\begin{tabularx}{\textwidth}{lrX}
\begin{tabu}{X[,l]X[,r]X[,l]}
\toprule
Name & Value & Description \hypertarget{Jwordbytes}{}\\
\midrule
$J_{\mathrm{wordbytes}}$ & 4  & This is the bytes in a word.}\hypertarget{Jdatasetinit}{}\\
$J_{\mathrm{datasetinit}}$ & $2^{30}$ & This is the bytes in the dataset at genesis. \hypertarget{Jdatasetgrowth}{}\\
$J_{\mathrm{datasetgrowth}}$ & $2^{23}$ & This is the dataset growth per epoch. \hypertarget{Jcacheinit}{}\\
$J_{\mathrm{cacheinit}}$ & $2^{24}$ & This is the bytes in the cache at genesis.\hypertarget{Jcachegrowth}{}\\
$J_{\mathrm{cachegrowth}}$ & $2^{17}$ & This is the cache growth per epoch.\hypertarget{Jepoch}{}\\
$J_{\mathrm{epoch}}$ & 30000 & This is the blocks per epoch.\hypertarget{Jmixbytes}{}\\
$J_{\mathrm{mixbytes}}$ & 128 & This is the mix length in bytes.\hypertarget{Jhashbytes}{}\\
$J_{\mathrm{hashbytes}}$ & 64 & This is the hash length in bytes.\hypertarget{Jparents}{}\\
$J_{\mathrm{parents}}$ & 256 & This is the number of parents of each dataset element.\hypertarget{Jcacherounds}{}\\
$J_{\mathrm{cacherounds}}$ & 3 & This is the number of rounds in cache production.\hypertarget{Jaccesses}{}\\
$J_{\mathrm{accesses}}$ & 64 & This is the number of accesses in a hashimoto loop.\\
\bottomrule
\end{tabu}
%\end{tabularx}

>>>>

%\begin{tabularx}{\textwidth}{lrX}
\begin{tabu}{X[,l]X[,r]X[,l]}
\toprule
Name & Value & Description \hypertarget{Jwordbytes}{}\\
\midrule
$J_{\mathrm{wordbytes}}$ & 4  & This is the bytes in a word.\hypertarget{Jdatasetinit}{}\\
$J_{\mathrm{datasetinit}}$ & $2^{30}$ & This is the bytes in the dataset at genesis. \hypertarget{Jdatasetgrowth}{}\\
$J_{\mathrm{datasetgrowth}}$ & $2^{23}$ & This is the dataset growth per epoch. \hypertarget{Jcacheinit}{}\\
$J_{\mathrm{cacheinit}}$ & $2^{24}$ & This is the bytes in the cache at genesis.\hypertarget{Jcachegrowth}{}\\
$J_{\mathrm{cachegrowth}}$ & $2^{17}$ & This is the cache growth per epoch.\hypertarget{Jepoch}{}\\
$J_{\mathrm{epoch}}$ & 30000 & This is the blocks per epoch.\hypertarget{Jmixbytes}{}\\
$J_{\mathrm{mixbytes}}$ & 128 & This is the mix length in bytes.\hypertarget{Jhashbytes}{}\\
$J_{\mathrm{hashbytes}}$ & 64 & This is the hash length in bytes.\hypertarget{Jparents}{}\\
$J_{\mathrm{parents}}$ & 256 & This is the number of parents of each dataset element.\hypertarget{Jcacherounds}{}\\
$J_{\mathrm{cacherounds}}$ & 3 & This is the number of rounds in cache production.\hypertarget{Jaccesses}{}\\
$J_{\mathrm{accesses}}$ & 64 & This is the number of accesses in a hashimoto loop.\\
\bottomrule
\end{tabu}
%\end{tabularx}
